---
title: "Community Trajectory Analysis (CTA) on Government Diatom Data Set"
author: "Muyeol Jung"
date: 22/05/20
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(vegan)
library(vegclust)
library(goeveg)
library(RColorBrewer)
library(smacof)
library(randomcoloR)
```

## Introduction

https://cran.r-project.org/web/packages/vegclust/vignettes/CTA.html#simple-example

For Govermnemt Diatom Data, the result of nMDS isn't well-presented in 2D base or 3d base plots, so Community Trajectory Analysis is brought in to geometrically show the direction and angle in dimensional plot.


## Data Process
Government Diatom Data (Spring and Autumn from 2009 to 2018)
1. Load
2. Select : drop columns (HalfofYear, Bio.Code.Name, Density)
3. Combine with Site Name and Create Stage by year
4. Convert to wide format
5. Extract Enviornment from the data

```{r}
# Load Government Data Set
Raw_GV_D <- read_csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Diatom_Data/Gov_Diatom_Percentage.csv")
#In order to import data from Github, URL for data must be "directoy" for RAW


# Select
GOV_DS <- Raw_GV_D %>% select(1,2,3,5,7)
rm(Raw_GV_D)


# Combine with Env by Bio Name column
GOV_D_Env <- read_csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Diatom_Data/Studysites_20190725.csv")

GOV_D_Env <- GOV_D_Env %>% select(-8, -10, -12:-16)
colnames(GOV_D_Env)[9] <- "Bio.Code"
Comb_GOV_Data <- left_join(GOV_D_Env, GOV_DS, by="Bio.Code")


# Convert to wideformat, miscellaneous
Wide_GOV_Data <- Comb_GOV_Data %>% spread(key = Species, value = Percent) %>% select(-421)
#key = Column, value = in the table
#421 column is NA value only

Weir_Data <- Wide_GOV_Data %>% filter(River.Type=="Weir") # Env contains weir location, so need to drop the column
Wide_GOV_Data <- Wide_GOV_Data %>% filter(River.Type!="Weir") # != for filter obs not containing

a <- Wide_GOV_Data %>% select(12:420)
a[is.na(a)]<-0

Final_GOV_Data <- Wide_GOV_Data %>% select(1:11) %>% cbind(a)
rm(a)
rm(Comb_GOV_Data, GOV_D_Env, GOV_DS, Wide_GOV_Data)


# Factors
## Half Of Year: Change 1/2 to Spring/Autumn
Final_GOV_Data$Half.Of.Year <- as.character(Final_GOV_Data$Half.Of.Year)
Final_GOV_Data$Half.Of.Year <- factor(Final_GOV_Data$Half.Of.Year, levels = c("1", "2"),
                                      labels = c( "Spring", "Autumn" ))

## New Code Name

Final_GOV_Data$New.Code.Name <-factor(Final_GOV_Data$New.Code.Name, levels = c(
  "M1", "M2","M3", "M4", "M5", "M6", "M7", "M8", "M9", "M10", "M11", "M12", "M13", "M14", "M15", "T1", "T2", "T3a", "T3b", "T4", "T5a", "T5b", "T6a", "T6b", "T7a", "T7b", "T8a", "T8b", "T9a", "T9b", "T10a", "T10b", "T11a", "T11b"))

## River Name
Final_GOV_Data$River.Name <- factor(Final_GOV_Data$River.Name, levels = c(
  "ND", "BB", "NS", "YG", "BS", "WE", "GM", "KH", "HO", "HG", "NG", "MR"))

Final_GOV_Data_M <- Final_GOV_Data %>% filter(River.Type=="M")
Final_GOV_Data_T <- Final_GOV_Data %>% filter(River.Type=="T")


#All_MY_D <- read_csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Final_Diatom_List_forAnalysis_datainput.csv")
```



## Analysis and Result

1. Determine dimensions
2. Stree plot
3. nMDS (performs Nonmetric Multidimensional scaling (metaMDS))
4. Community Trajectory Analysis (CTA) using nMDS (You can choose different types of multidimensional scaling methods)
5. Visualise them
6. Statistical Analysis (figures)

### Determine dimensions
```{r}
#Extract Env from all data (Final Gov Data Set)
Final_GOV_Env <- Final_GOV_Data %>% select(1:11)
Final_GOV_Species <- Final_GOV_Data %>% select(-1:-11)

# Determine the dimension
dimcheckMDS(Final_GOV_Species, distance="bray") #goeveg package

```

Stress value is 0.215, just over the boundary at 3 dimension. As a result, 3 dimensional space is selected for nMDS with extra care in interpretation.

Note.

Certainly, there are too many species present and some of which are not significant.
Perhaps, I could trim the dataset down with species less than 5%, then will it see an improvement in stress value?

### Stress plot for Main stream and nMDS
```{r}
#meta MDS: non Metrical multidimensional scaling
Final_ordination <- metaMDS(Final_GOV_Species, distance = "bray", k=3)
stressplot(Final_ordination)

```

What are the line

### Stress plot for Main / Tributaries and nMDS
```{r}
# Mainstream Stress value
m <- Final_GOV_Data_M %>% select(-1:-11)
dimcheckMDS(m)

m_ordination <- metaMDS(m, distance = "bray", k=3)
stressplot(m_ordination)

# m (alone): stress value: 0.21 at 3 dimension

# Tributaries Stress value
t <- Final_GOV_Data_T %>% select(-1:-11)
dimcheckMDS(t)

t_ordination <- metaMDS(t, distance = "bray", k=3)
stressplot(t_ordination)

# t (alone): stress value: 0.21 at 3 dimension
```

Diatom data set for Spring / Autumn
Mainstream and Tributaries both have 0.21 stress value at 3 dimensions and at dimension 4, the value falls within the boundary.

For this experiment, 3 dimension is selected!

## Community Trajectory Analysis (CTA)

I created nMDS, one of multivariate analysis, ordination dimension reduction 


#### Final ordination: Gov Data
```{r}
# Extract location of samples in dimensional space
Fn_Ordi_Point3d <- data.frame(X=Final_ordination$points[,1],
                                 Y=Final_ordination$points[,2],
                                 Z=Final_ordination$points[,3]
                                 )
Fn_Ordi_nMDS_Result <- cbind(Fn_Ordi_Point3d, Final_GOV_Env)
```

#### Four square plots Spring/Autumn x Main/tributaries
```{r}
# by River Type
Fn_Ordi_nMDS_Result %>% ggplot(aes(X, Y, colour=Z))+
  geom_point()+
  geom_vline(xintercept = 0, linetype=2, color="red")+
  geom_hline(yintercept = 0, linetype=2, color="red")+
  theme_bw()+
  facet_grid(Half.Of.Year~River.Type)

# by River Type ~ Year
Fn_Ordi_nMDS_Result %>% ggplot(aes(X, Y, color=as.factor(Year)))+
  geom_point(size=2)+
  geom_vline(xintercept = 0, linetype=2, color="red")+
  geom_hline(yintercept = 0, linetype=2, color="red")+
  theme_bw()+
  facet_grid(Half.Of.Year~River.Type)

# by River Name (M+T)
Fn_Ordi_nMDS_Result %>% ggplot(aes(X, Y, colour=Z))+
  geom_point()+
  geom_vline(xintercept = 0, linetype=2, color="red")+
  geom_hline(yintercept = 0, linetype=2, color="red")+
  theme_bw()+
  facet_grid(Half.Of.Year~River.Name)

## Mainstream
Fn_Ordi_nMDS_Result %>% filter(River.Type=="M") %>% 
  ggplot(aes(X, Y, colour=Z))+
  geom_point()+
  geom_vline(xintercept = 0, linetype=2, color="red")+
  geom_hline(yintercept = 0, linetype=2, color="red")+
  theme_bw()+
  facet_grid(Half.Of.Year~River.Name)

## Tributaries
Fn_Ordi_nMDS_Result %>% filter(River.Type=="T") %>% 
  ggplot(aes(X, Y, colour=Z))+
  geom_point()+
  geom_vline(xintercept = 0, linetype=2, color="red")+
  geom_hline(yintercept = 0, linetype=2, color="red")+
  theme_bw()+
  facet_grid(Half.Of.Year~River.Name)
```


#### Main stream: all sites in one graph

```{r}
#https://www.reed.edu/data-at-reed/resources/R/loops_with_ggplot2.html ggplot loops

Fn_nMDS_M <- Fn_Ordi_nMDS_Result %>% filter(River.Type =="M") 
Fn_nMDS_M_Site <- Fn_nMDS_M$New.Code.Name
Fn_nMDS_M_Year <- Fn_nMDS_M$Year
Fn_nMDS_M_Survey <- Fn_nMDS_M$Half.Of.Year

# Spring / Autumn (select)
## Spring
ggplot(data=subset(Fn_nMDS_M, Half.Of.Year=="Spring"), aes(X, Y, color=New.Code.Name))+
  geom_point()+
  geom_path()+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+geom_vline(xintercept = 0, lty= 2, color="red")+
  labs(title="nMDS results of Government Data Set",
       subtitle = "Spring Diatom Data Set in Mainstream", 
       caption = "Data Source: Government Data Set")

## Autumn
ggplot(data=subset(Fn_nMDS_M, Half.Of.Year=="Autumn"), aes(X, Y, color=New.Code.Name))+
  geom_point()+
  geom_path()+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+geom_vline(xintercept = 0, lty= 2, color="red")+
  labs(title="nMDS results of Government Data Set",
       subtitle = "Autumn Diatom Data Set in Mainstream", 
       caption = "Data Source: Government Data Set")

# Spring / Autumn (facet wrap)
Fn_nMDS_M %>%
  ggplot(aes(X, Y, color=Fn_nMDS_M_Site))+
  geom_point()+
  geom_path()+
  geom_text(label=Fn_nMDS_M_Year, size=3, nudge_y=0.1, check_overlap = T)+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+geom_vline(xintercept = 0, lty= 2, color="red")+
  labs(title="nMDS results of Government Data Set",
       subtitle = "Spring and Autumn Diatom Data Sets in Mainstream", 
       caption = "Data Source: Government Data Set")+
  facet_wrap(~Half.Of.Year)

```


#### Main stream: each site in one graph, but one line in facet grid
```{r}
# All facet grid: hard to read
ggplot(Fn_nMDS_M, aes(X, Y, colour=Z))+
  geom_point(size=1)+
  geom_path()+
  geom_text(label=Fn_nMDS_M_Year, size=2, check_overlap = T)+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+
  geom_vline(xintercept = 0, lty= 2, color="red")+
  labs(title = "Comparisons of nMDS results between Spring and Autumn Diatom Data Sets",
       caption = "Data Source: Government Data Set")+
  facet_grid(Half.Of.Year~New.Code.Name)

```

Compare spring and Autumn trajectory?

#### Main stream: facet_grid 5 sites in one graph for better resolutions
```{r}
# M1-M5 extraction
Fn_M1M5 <-Fn_nMDS_M %>% filter(New.Code.Name=="M1"|New.Code.Name=="M2"|New.Code.Name=="M3"|New.Code.Name=="M4"|New.Code.Name=="M5")
Fn_M1M5_Year <- Fn_M1M5$Year

# M6-M10 extraction
Fn_M6M10 <-Fn_nMDS_M %>% filter(New.Code.Name=="M6"|New.Code.Name=="M7"|New.Code.Name=="M8"|New.Code.Name=="M9"|New.Code.Name=="M10")
Fn_M6M10_Year <- Fn_M6M10$Year

# M11-M15 extraction
Fn_M11M15 <-Fn_nMDS_M %>% filter(New.Code.Name=="M11"|New.Code.Name=="M12"|New.Code.Name=="M13"|New.Code.Name=="M14"|New.Code.Name=="M15")
Fn_M11M15_Year <- Fn_M11M15$Year

# M1-M5 ggplot
ggplot(Fn_M1M5, aes(X, Y, colour=Z))+
  geom_point(size=1)+
  geom_path()+
  geom_text(label = Fn_M1M5_Year, size=2, nudge_y = 0.1, check_overlap = T)+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+
  geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_grid(Half.Of.Year~New.Code.Name)+
  labs(title = "nMDS results: M1 - M5")

# M6-M10 ggplot
ggplot(Fn_M6M10, aes(X, Y, colour=Z))+
  geom_point(size=1)+
  geom_path()+
  geom_text(label = Fn_M6M10_Year, size=2, nudge_y = 0.1, check_overlap = T)+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+
  geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_grid(Half.Of.Year~New.Code.Name)+
  labs(title = "nMDS results: M6 - M10")
# M11-M15 ggplot
ggplot(Fn_M11M15, aes(X, Y, colour=Z))+
  geom_point(size=1)+
  geom_path()+
  geom_text(label = Fn_M11M15_Year, size=2, nudge_y = 0.1, check_overlap = T)+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+
  geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_grid(Half.Of.Year~New.Code.Name)+
  labs(title = "nMDS results: M11 - M15")
```





#### Main stream: each site in one graph using facet wrap

```{r}
# M1-M15 Spring / Autumn + Facet_wrap

ggplot(data=subset(Fn_nMDS_M, Half.Of.Year=="Spring"), aes(X, Y, color=Z))+
  geom_point()+
  geom_path()+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_wrap(~New.Code.Name, ncol=5)

ggplot(data=subset(Fn_nMDS_M, Half.Of.Year=="Autumn"), aes(X, Y, color=Z))+
  geom_point()+
  geom_path()+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_wrap(~New.Code.Name, ncol=5)


## Comparison between Spring and Autumn Data in one facet wrap graph (3 dimensions omiited)
Com_plot <- ggplot(Fn_nMDS_M, aes(X, Y, color=Half.Of.Year))+
  geom_point()+
  geom_path()+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_wrap(~New.Code.Name, ncol=5)

Com_plot+ geom_text(data = Fn_nMDS_M, label=Fn_nMDS_M$Year, size=2, nudge_y = 0.2, check_overlap = T)+
  labs(title = "nMDS results of Spring and Autumn Data Set")

## Selective labelling with ggplot2

ggplot(Fn_nMDS_M, aes(X, Y, colour=Z, label=Year))+
  geom_point(size=1)+
  geom_path()+
  geom_text(data=subset(Fn_nMDS_M, Year > 2017 | Year < 2010), size=3,nudge_y = 0.2, check_overlap = T)+
  theme_bw()+
  geom_hline(yintercept = 0, lty= 2, color="red")+
  geom_vline(xintercept = 0, lty= 2, color="red")+
  facet_wrap(~New.Code.Name, ncol=5)

```
