---
title: "Replicability of Diatoms: Dissimilarity of First 15 Diatom Sampes in the Nakdong River, South Korea"
author: "Muyeol Jung"
date: "31/07/2020"
output:
  github_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vegan)
library(tidyverse)
library(ggplot2)
library(reshape2)
```

# Introduction

Diatoms have been widely used in water qualty assessment because of their traits of sensitivity to changes in environments and ubiquity in water. Kelly and other researchers have adapted diatom to water quality analysis, however, how replicable diatoms are remain unanswered.

This chapter is to attempt to compare daitom samples taken at the same time from different rock samples and to examine their replicability in random selection. For the research purpose, all 15 rock samples were collected at three major different sites in Nakdong River Dec 2018, encompassing upstream, midstream and downstream.

Methodologically, dissimilarity between samples is calculated and then plotted using non-metric Multidimensional scaling.




# Data Process and Analysis

## Import Dataset and Process

Diatom Counts from 15 rock sample are imported and then processed in an appropriate format of table with observations in rows and species in columns.

```{r echo=T, results='hide'}
# Import the data set and transpose
D15.Count <- read.csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Rex/Final_Diatom_List.csv", stringsAsFactors = FALSE) %>% t()


# Convert matrix to dataframe
D15.Count <- data.frame(data.matrix(D15.Count))
#summary(D15.Count)

# colnames
D15_colname <- D15.Count[1,]
D15_colname <- lapply(D15_colname, as.character)

D15.Count <- D15.Count[-1,]

## Convert factors to numeric
index <- sapply(D15.Count, is.factor)
D15.Count[index] <- lapply(D15.Count[index], function(x) as.numeric(as.character(x)))

colnames(D15.Count) <- D15_colname
rm(D15_colname, index)

# Complete: D15.Count

# Create Species list with relative abundance (All)

D15_Spec_abundance <- colSums(D15.Count) %>% data.frame()
colnames(D15_Spec_abundance)[1] <- "Count"
D15_Spec_abundance$Species <- rownames(D15_Spec_abundance)
rownames(D15_Spec_abundance) <- NULL
D15_Spec_abundance <- D15_Spec_abundance[, c(2,1)]
D15_Spec_abundance <- D15_Spec_abundance %>% mutate(Percent = Count/sum(Count)*100)
arrange(D15_Spec_abundance, desc(Percent))

### below also works -------

#D15.Count1 <- read.csv("Final_Diatom_List.csv") %>% t()
#D15.Count1 <- data.frame(data.matrix(D15.Count1))

#a1 <- D15.Count1[1,]
#a1 <- lapply(a1, as.character)

#D15.Count1 <- D15.Count1[-1,]
#colnames(D15.Count1) <- a1

#D15.Count1

#index <- sapply(D15.Count1, is.factor)
#D15.Count1[index] <- lapply(D15.Count1[index], function(x) as.numeric(as.character(x)))


# Convert to Per centage (Cont. from above)
Site <- rownames(D15.Count) %>% data.frame()
colnames(Site)[1] <- "Site"
row.names(D15.Count) <- NULL

D15 <- cbind(Site, D15.Count)
rm(Site, D15.Count)

# convert to Long format
Long_D15 <- melt(D15, na.rm=FALSE, id.vars = "Site", variable.name = "Species", value.name = "Count")
Long_D15 <- Long_D15 %>% group_by(Site) %>% 
  mutate(Percent= Count/sum(Count, na.rm = TRUE)*100)

# Check the sum
Long_D15 %>% group_by(Site) %>% summarise(Total = sum(Percent, na.rm = TRUE))

# Convert back to Wide format
Wide_D15 <- Long_D15 %>% select(-3) %>% dcast(Site~Species)

rm(D15, Long_D15)

# Complete: Final data -> Wide_D15
```



## Import Environment Dataset for the sampling data

Environmental data for the diatom results are also loaded.
The data includes Name, Site(Group), and Date and Site will be used here as grouping factor.

Site; A upstream, B midstream, C downstream

```{r echo=T, results='hide'}
# Import Environment dataset
D15_env <- read.csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Diatom_Data/Diatom15_Env.csv")

# Combine it with the precessed D15 Dataset
D15 <- inner_join(Wide_D15, D15_env, by="Site")
rm(D15_env, Wide_D15)

# Re-order columns
D15 <- D15[,c(1,237:240, 2:236)] 

# For analysis, Env and Species are split seperately
D15_Species <- D15 %>% select(6:240)
D15_Env <- D15 %>% select(1:5)

# Save D15 file as separate csv file for future use 
# write.csv(D15, "D:/Rmarkdown/D15_Data.csv")
```




# Results

1. nMDS Analysis: collapse data into low dimensional spaces
- Check dimension
- Create ordination and check Stress plot
- Draw plot

2. Post hoc Analysis: Analysis of Similiarities (ANOSIM)
- Calculate distance (Bray)
- Within and among group distances

## nMDS analysis
```{r}
# dimension check for nMDS
goeveg::dimcheckMDS(D15_Species) # goeveg package
# Solution reached, stress value 0.051629323 at 2 dimension

# Create ordination based on the selected dimensions
D15_Ordination <- metaMDS(D15_Species, distance = "bray", k=2)
stressplot(D15_Ordination) # Stress plot for it
# Non-meteric fit R2 = 0.997, Linear fit R2 = 0.989


plot(D15_Ordination)

#D15.ordination <- metaMDS(D15.Count, distance = "bray", k=2)
#plot(D15.ordination, type="t", display = "sites")
#with(D15.env, ordihull(D15.ordination, Site))
```


```{r}
# Extract nMDS results for visualisation
## nMDS Point (Site): nMDS_point_D15
D15_nMDS_point <- scores(D15_Ordination, display = "sites", shrink = FALSE, choices = c(1,2)) %>% data.frame()
nMDS_point_D15 <- cbind(D15_nMDS_point, D15_Env) # Combine with Env for visualisation
rm(D15_nMDS_point)

## D15 Species
D15_nMDS_species <- scores(D15_Ordination, display = "species", shrink = FALSE, choices = c(1, 2)) %>%
  data.frame() %>% drop_na()
# Make Species column in df
D15_nMDS_species$Species <- rownames(D15_nMDS_species)
rownames(D15_nMDS_species) <- NULL

### combine species point with abundance data 
nMDS_Species_abun_D15 <- inner_join(D15_nMDS_species, D15_Spec_abundance, by="Species")
rm(D15_nMDS_species, D15_Spec_abundance)

# Final complete df; nMDS_point_D15 and nMDS_Species_abun_D15


# Create Plots #

# Plot nMDS Site location with 95% confidence ellipse
Plot_D15_nMDS_Site <- 
ggplot(nMDS_point_D15, aes(x=NMDS1, y=NMDS2, colour=Group, label=Number))+
  geom_point(size=3)+
  geom_text(size=4, color="black", hjust=0, vjust=0)+
  geom_vline(xintercept = 0, linetype="dotted")+
  geom_hline(yintercept = 0, linetype="dotted")+
  #xlim(-0.75, 0.5)+
  theme_bw()+
  stat_ellipse(geom = "path", type = "t", level = 0.95)+
  theme(legend.position = c(0.1, 0.2),
        legend.background = element_rect(size=0.5, linetype="solid"))

# type: euclid: draws a circle with the radius equal to level
# segment: the number of edges in ellipse
ggsave("Plot_D15_nMDS_Site.png", type="cairo", dpi = 500, height = 10, units = "cm")


# Plot nMDS species (all species)
Plot_D15_nMDS_Spe <-
ggplot(nMDS_Species_abun_D15, aes(x=NMDS1, y=NMDS2, label=nMDS_Species_abun_D15$Species))+
  geom_point(size=1.5, shape = 3, color="red")+
  geom_text(size=1, color="black", hjust=0.5, vjust=0.5, angle=45)+
  geom_vline(xintercept = 0, linetype="dotted")+
  geom_hline(yintercept = 0, linetype="dotted")+
  theme_bw()
ggsave("Plot_D15_nMDS_Spe.png", type="cairo", dpi = 500, height = 10, units = "cm")

# Plot nMDS species (excluding low abundant ones)
Plot_D15_nMDS_Spe_High <-
ggplot(data=subset(nMDS_Species_abun_D15, Percent>=0.5), 
       aes(x=NMDS1, y=NMDS2, label=Species))+
  geom_point(size=1.5, shape = 3, color="red")+
  geom_text(size=1, color="black", hjust=0.5, vjust=0.5, angle=45)+
  geom_vline(xintercept = 0, linetype="dotted")+
  geom_hline(yintercept = 0, linetype="dotted")+
  theme_bw()
ggsave("Plot_D15_nMDS_Spe_High.png", type="cairo", dpi = 500, height = 10, units = "cm")


# Merge two plots above; Site + Species
Plot_D15_Site_SpeH <- ggpubr::ggarrange(Plot_D15_nMDS_Site, Plot_D15_nMDS_Spe_High) #,legend = "bottom")
ggsave("Plot_D15_Site_SpeH.png", type="cairo", dpi = 500, height = 10, units = "cm")



# Plot two dataset in one graph; nMDS_point_D15 and nMDS_Species_abun_D15
# Set a condition first
Percent_1 <- nMDS_Species_abun_D15$Percent>=1


# Next, plot
Plot_D15_Allone <-
  ggplot()+
  geom_point(data=nMDS_point_D15, aes(x=NMDS1, y=NMDS2, colour=Group, label=Number), size=4)+
  geom_text(data=nMDS_point_D15, aes(x=NMDS1, y=NMDS2, label=Number), size=3, color="black", hjust=0.5, vjust=0.5)+
  geom_point(data=nMDS_Species_abun_D15,
             aes(x=NMDS1, y=NMDS2, shape=Percent_1), color="grey50", size=2)+
  scale_shape_manual(values = c(3,20), name = "Species", label= c("<1% (N=160)", ">=1% (N=31)"))+
  #N check!!! 31/191)
  ggrepel::geom_text_repel(data = subset(nMDS_Species_abun_D15, Percent>=1),
                           aes(x=NMDS1, y=NMDS2, label=Species),
                           size=3, segment.size = 0.2, force = 1, max.iter = 3000)+
  geom_hline(yintercept = 0, linetype=2, color="black")+
  geom_vline(xintercept = 0, linetype=2, color="black")+
  theme_bw()+
  theme(legend.position = "bottom")+
  scale_colour_discrete(name = "Site")
#+annotate("text", x=-.75, y=-1.0, label= "N of Species >= 1%  = 31/191", size=3)
#  theme(legend.position = c(0.1, 0.2),
#       legend.background = element_rect(size=0.5, linetype="solid"))

ggsave("Plot_D15_Allone.png", type="cairo", dpi = 500, width = 20, units = "cm")
 
# Seperately, it works, but combined, then scaleshape manual don't work

Subset_spec_05 <- subset(nMDS_Species_abun_D15, Percent>=0.5) # 46 Species
Subset_spec_1 <- subset(nMDS_Species_abun_D15, Percent>=1) # 31 Species

```


## Analysis of Similarities(ANOSIM)

1. Calculate distance
2. Compare it through ANOSIM



Calculate dissimilarities: vegdist (Dissimilarity Indicies for Community Ecologists)

Command "Vegdist" will calculate distances (dissimilarity) between observations (samples).
The Bray-Curtis distance is used as the Bray-Curtis dissimilarity is one of the most well-known ways of quantifying the difference between samples. (It does not satisfy the triangle inequality axiom, and hence is not a true distance)

Bray-Curtis distance is calculated as follows.

$$d_{j,k}= \sqrt{\frac{\sum _i|x_ij-x_ik|}{\sum _i(x_ij+x_ik)} }$$
where $x_ij$, $x_ik$ refer to the quantity on species (column) $i$ and site (rows) $j$ and $k$.

Bray-Curtis distance scale (multiply 100) is easy to understand (0 means the samples are exactly the same, while 100 is the maximum difference that can be observed between two samples).

Here, dissimilarities are calculated on raw counts (not relative abundance).

```{r}
# Calculate distance

# columns where all values are 0 don't affect distance at all
D15_Dist <- vegdist(D15_Species, method = "bray")
```


ANOSIM provides a way to test statistically whether there is a significant difference between two or more groups of sampling units. It operates directly on a dissimilarity matrix. (uses only the rank order of dissimilarity values)

```{r}
# ANOSIM analysis
D15_Dist_Anosim <- with(D15_Env, anosim(D15_Dist, Group)) 

summary(D15_Dist_Anosim)
plot(D15_Dist_Anosim)


# Anosim: 1. calcuate a matrix of dissimiliarities scores for every pair of sites
# 2. convert the dissimiliarities to ranks
# 3. calculate the R statistic as the ratio between dissimilarities between sites within a group (e.g. high grazing pressure) and the dissimilarities between sites that are in different groups. The closer this value is to 1, the more the sites within a group are similar to each other and dissimilar to sites in other groups.
# 4. The significance of the R-statistic is determined by permuting the membership of sites in groups.
# The closer to 1, the more similar to each other within the group and the more dissimilar to sites in other groups


#
# When you print the result of ANOSIM  (I am assuming here that you used vegan)
# you get 
# 1) the global R value (the test statistics for ANOSIM) followed by the p-value 
# 2) The type of permutation done and the number of permutation 
# 3) distribution of the test statistic (R) obtained under the null hypothesis. This can equally be shown graphically as histograms. But in vegan you get numerical summaries of R as quantiles 
# 4) finally you get summary of the between group and within group rank dissimilarities.

# Here too you get the distributional summaries of A) the between group rank dissimilarities  from the minimum (0%) to the maximum (100%) B) the within group rank dissimilarity from the minimum (0%) to the maximum (100%) C) the number of observation (replicates) "N".



# Extract Anosim data from the result (D15_Dist_Anosim) for a better visualisation
a <- D15_Dist_Anosim$dis.rank %>% data.frame()
b <- D15_Dist_Anosim$class.vec %>% data.frame()

colnames(a)[1] <- "Dis.rank"
colnames(b)[1] <- "Class"

D15_Anosim_t <- cbind(b, a)

ggplot(D15_Anosim_t, aes(x=Class, y=Dis.rank))+geom_boxplot(outlier.colour="black", outlier.shape=16,
             outlier.size=2, notch=TRUE)+
  theme_bw()+xlab("Group")+ylab("Dissimilarity rank") 
                                                                                 
ggsave("D15_Anosim.png", type="cairo", dpi = 500, height = 10, units = "cm")

# This needs understanding, generally the mean of this plot: about dissimilarity rank
ggplot(D15_Anosim_t, aes(x=Class, y=Dis.rank))+geom_dotplot(binaxis='y', stackdir='center', dotsize=1)+
  theme_bw()+xlab("Group")+ylab("Dissimilarity rank") 

# Notch explained
# http://www.sthda.com/english/wiki/ggplot2-box-plot-quick-start-guide-r-software-and-data-visualization



D15.anosim <- with(D15.env, anosim(D15.Count.dist, Site))
summary(D15.anosim)
plot(D15.anosim)

```




## MRPP: Multi Response Permutation Procedure and Mean Dissimilarity Matrix

mrpp for a similar function using original dissimiliarities instead of their ranks.

```{r pressure, echo=FALSE}
D15_Dist_Mrpp <- with(D15_Env, mrpp(D15_Species, distance = "bray", Group))
D15_Dist_Mrpp

D15_Dist_Mrpp_E <- with(D15_Env, mrpp(D15_Species, distance = "euclidean", Group))
D15_Dist_Mrpp_E

# Mean Distance within/between groups
D15_Dist_Mean_dis <- with(D15_Env, meandist(D15_Dist, Group))
D15_Dist_Mean_dis

# Summary finds the within-class, between class and overall means of these dissimiliarities
summary(D15_Dist_Mean_dis)
plot(D15_Dist_Mean_dis)



#D15.mrpp <- with(D15.env, mrpp(D15.Count, distance = "bray", Site))
#D15.mrpp

#D15.mrpp_E <- with(D15.env, mrpp(D15.Count, distance = "euclidean", Site))
#D15.mrpp_E

## mean distance within/between groups
#D15.meandis <- with(D15.env, meandist(D15.Count.dist, Site))
#D15.meandis

# summary finds the within-class, between-class and overall means of these dissimilarities.
#summary(D15.meandis)
#plot(D15.meandis)
```


### Conclusion

On Bray-Curtis dissimilarities, fives samples at each site are clustered, whereas far away from samples from other sites.

Samples at site C are more closely clustered followed by site A, site B is the least clustered.
