---
title: "Data Cleaning for Species Percentage List"
author: "Muyeol Jung"
date: 18/09/20
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(vegan)
library(vegclust)
library(goeveg)
library(RColorBrewer)
library(smacof)
library(randomcoloR)
library(matrixStats)
```

## Introduction

https://cran.r-project.org/web/packages/vegclust/vignettes/CTA.html#simple-example

GOVD have 399 species in the study area. 
Need to extract some species that have more meaning than others and can tell me what are true story happeneing behind all species.

Therefore, species selected greater than 0.1, 0.5, 1% are put into analysis for how the original structure show in Dimensional Check.


## Data Process
Government Diatom Data (Spring and Autumn from 2009 to 2018)
1. Load
2. Select : drop columns (HalfofYear, Bio.Code.Name, Density)
3. Combine with Site Name and Create Stage by year
4. Convert to wide format
5. Extract Enviornment from the data

```{r}
# Load Government Data Set
Raw_GV_D <- read_csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Diatom_Data/Gov_Diatom_Percentage.csv")
#In order to import data from Github, URL for data must be "directoy" for RAW


# Select
GOV_DS <- Raw_GV_D %>% select(1,2,3,5,7)
rm(Raw_GV_D)


# Combine with Env by Bio Name column
GOV_D_Env <- read_csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Diatom_Data/Studysites_20190725.csv")

GOV_D_Env <- GOV_D_Env %>% select(-8, -10, -12:-16)
colnames(GOV_D_Env)[9] <- "Bio.Code"
Comb_GOV_Data <- left_join(GOV_D_Env, GOV_DS, by="Bio.Code")


# Convert to wideformat, miscellaneous
Wide_GOV_Data <- Comb_GOV_Data %>% spread(key = Species, value = Percent) %>% select(-421)
#key = Column, value = in the table
#421 column is NA value only

Weir_Data <- Wide_GOV_Data %>% filter(River.Type=="Weir") # Env contains weir location, so need to drop the column
Wide_GOV_Data <- Wide_GOV_Data %>% filter(River.Type!="Weir") # != for filter obs not containing

a <- Wide_GOV_Data %>% select(12:420)
a[is.na(a)]<-0

b <- Wide_GOV_Data %>% select(1:11) %>% mutate(Stage = case_when(Year >= 2009 & Year <= 2011 ~ "During",
                        Year >= 2012 & Year <= 2018 ~ "Post"))

# Remove columns where all values are 0
a <- a %>% select_if(colSums(.) != 0) #409 columns -> 399

Final_GOV_Data <- cbind(b,a)
rm(a, b)
rm(Comb_GOV_Data, GOV_D_Env, GOV_DS, Wide_GOV_Data)

# Factors
## Half Of Year: Change 1/2 to Spring/Autumn
Final_GOV_Data$Half.Of.Year <- as.character(Final_GOV_Data$Half.Of.Year)
Final_GOV_Data$Half.Of.Year <- factor(Final_GOV_Data$Half.Of.Year, levels = c("1", "2"),
                                      labels = c( "Spring", "Autumn" ))

## Stage
Final_GOV_Data$Stage <- factor(Final_GOV_Data$Stage, levels = c("During", "Post"))

## New Code Name
Final_GOV_Data$New.Code.Name <-factor(Final_GOV_Data$New.Code.Name, levels = c(
  "M1", "M2","M3", "M4", "M5", "M6", "M7", "M8", "M9", "M10", "M11", "M12", "M13", "M14", "M15", "T1", "T2", "T3a", "T3b", "T4", "T5a", "T5b", "T6a", "T6b", "T7a", "T7b", "T8a", "T8b", "T9a", "T9b", "T10a", "T10b", "T11a", "T11b"))

## River Name
Final_GOV_Data$River.Name <- factor(Final_GOV_Data$River.Name, levels = c(
  "ND", "BB", "NS", "YG", "BS", "WE", "GM", "KH", "HO", "HG", "NG", "MR"))

Final_GOV_Data_M <- Final_GOV_Data %>% filter(River.Type=="M")
Final_GOV_Data_T <- Final_GOV_Data %>% filter(River.Type=="T")


#All_MY_D <- read_csv("https://raw.githubusercontent.com/muyeoljung/Diatom-Data-Analysis/master/Final_Diatom_List_forAnalysis_datainput.csv")
```



## Analysis and Result

1. Determine dimensions
2. Stree plot
3. nMDS (performs Nonmetric Multidimensional scaling (metaMDS))
4. Community Trajectory Analysis (CTA) using nMDS (You can choose different types of multidimensional scaling methods)
5. Visualise them
6. Statistical Analysis (figures)

### Data Separation: Species and Env
```{r}
#Extract Env from all data (Final Gov Data Set)
Final_GOV_Env <- Final_GOV_Data %>% select(1:12)
Final_GOV_Species <- Final_GOV_Data %>% select(-1:-12)
```


### Create a DF with proportion per species
```{r}
#What I want to do is that select all columns (Species) where the proportion is greater than 5 %

bind_cols(Species=colnames(Final_GOV_Species), Total=(colSums(Final_GOV_Species)))->species # Column-wise sum

species <- species %>% mutate(Prop=Total/sum(Total)*100)

species %>% filter(Prop>0.5) %>% arrange(Prop)

write.csv(species, "D:/Rmarkdown/Species_prop.csv") # Save as csv
# This is the list of diatom speices in Data Set with proportion of its species
# This can be saved and later used for research later.

# However, analysis further down is to show how exclusion of species at certain level of proportion will affect stress value level.

```


### Create DFs for dimensions check
```{r}
# data: Final_GOV_Species (ignore the others)

a <- colSums(Final_GOV_Species) # Sum of each column
b <- sum(a) # Sum of sums up of all species (total)
ab <- a/b*100 # proportion of each species

Cond_1 <- ab > 0.1 #proportion is greater than 0.1% 81 species
Cond_2 <- ab > 0.5 #proportion is greater than 0.5% 37 species
Cond_3 <- ab > 1.0 #proportion is greater than 1% 23 species


Sel_01 <- Final_GOV_Species[,Cond_1, drop=FALSE] # DF for Cond 1 # 81 species
Sel_05 <- Final_GOV_Species[,Cond_2, drop=FALSE] # DF for Cond 2 # 37 species
Sel_1 <- Final_GOV_Species[,Cond_3, drop=FALSE] # DF for Cond 3 # 23 species


# Species that are greater than 0.1 with "Other" categories removed.
Cond_4 <- grepl("(other)", colnames(Sel_01))
Sel_01_rm_lump <- Sel_01[,!Cond_4, drop=FALSE]  # using ! before condition, the reverse function can be implemented.

# Based on False/True, want to select only columns which are TRUE from original data (Final_GOV_Speices)

```


### Check dimension and stress value for eash data set
```{r}
dimcheckMDS(Sel_01_rm_lump) # 4d: 77 species (0.1 except lump) 0.4241538 0.2798009 0.2110374 0.1678039 0.1395913 0.1227646
dimcheckMDS(Sel_01) # 0.1%, 4d : 81 species
dimcheckMDS(Sel_05) # 0.5%, 4d: 37 species
dimcheckMDS(Sel_1) # 1%, 3d: 23 species

```

Conclusion
* With 1% (23 species) extracted from 399 species, stress value drops within a boundary (0.2) at 3 dimensional space
  * However, 23 species across more than 30 sites aren't enough numbers to effectively show the diversity.
* With 0.5% (37 species) extracted, stress value falls on a boundary at 3 dimensional space.
  * Still 37 species across more than 30 sites aren't enough
* With 0.1% (81 species) extracted, stress value falls within a boundary at 4 dimensional space.
  * However, it contains 4 lump categories that needs a review.
  * Sum of species that are greater than 0.1 is 94.56%
* With 0.1% with 4 lumped removed (77 species), stress value is almost the same as the original data.
  * Therefore, lumped categories don't affect the shape, and it can be removed as we don't know what exact species they are.


### Check Percentage of species selected 
```{r}
species %>% filter(Prop>1) %>% summarise(Total=sum(Prop)) #73.5 %
species %>% filter(Prop>0.5) %>% summarise(Total=sum(Prop)) # 84.1 %
species %>% filter(Prop>0.1) %>% summarise(Total=sum(Prop)) # 94.5 %
species %>% filter(Prop>0.1) %>% filter(!grepl("(other)", Species)) %>% summarise(Total=sum(Prop)) # 93.7 %
```
