---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Lock5Data)
library(boot)
library(ggplot2)
library(tidyverse)
```

## Introduction

## Example: Chapter 3 Bootstrap examples

1. Bootstrap Confidence Intervals with Standard Errors

```{r}
data("CommuteAtlanta")
str(CommuteAtlanta)
```



To construct the confidence interval for the mean commute time in Atlanta, we need to find the point estimate (sample mean) from the original sample.



```{r}
time.mean <- with(CommuteAtlanta, mean(Time))
time.mean
```


To find the standard error, we will create a huge matrix with 1000 rows and 500 columns. We will then use apply() to apply mean() to each row of the matrix.
```{r}
B <- 1000
n <- nrow(CommuteAtlanta)
boot.samples <- matrix(sample(CommuteAtlanta$Time, size = B*n, replace = TRUE), B, n)
```



apply()


```{r}
boot.statistics <- apply(boot.samples, 1, mean)
```





```{r}
data.frame(meanTime= boot.statistics)

ggplot(data.frame(meanTime = boot.statistics), aes(x=meanTime))+geom_histogram(binwidth = 0.25, aes(y=..density..))+geom_density(color="red")
```

```{r}
time.se <- sd(boot.statistics)
time.se
```

Finally, construct the confidence interval. Here I round the margin of error up and to one decimal place so that it has two significant digits, and I am being cautious when rounding not to make the interval too small.

```{r}
me <- ceiling(10*2*time.se)/10
round(time.mean, 1) + c(-1,1)*me
```


```{r}
my.mean <- function(x, indicies) {
  return(mean(x[indicies]))
}

time.boot <- boot(CommuteAtlanta$Time, my.mean, 10000)
#Boot(Original data, a function, and the number of bootstrap replicates)

boot.ci(time.boot)
```



## Import my data set

```{r}
setwd("J:/Rex")
D15.Count <- read.csv("Diatom15_Results.csv", stringsAsFactors = FALSE) %>% select(-1, -3) %>% arrange(Species) %>% t()
colnames(D15.Count) <-D15.Count[1,]
D15.Count <- D15.Count[-1,]
D15.Count.df <- data.frame(data.matrix(D15.Count))
index <- sapply(D15.Count.df, is.factor)
D15.Count.df[index] <- lapply(D15.Count.df[index], function(x) as.numeric(as.character(x)))
D15.Count.df[is.na(D15.Count.df)] <-0
```

